% research_cv.tex
% Compile with XeLaTeX

\documentclass[11pt,a4paper]{article}

% ===================== Fonts / Engine =====================
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}

% ===================== Layout =====================
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlist[itemize]{leftmargin=1.2em, noitemsep, topsep=2pt}
\renewcommand{\arraystretch}{1.15}

\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% ===================== Helpers =====================
\newcommand{\Link}[2]{\href{#1}{\texttt{#2}}}
\newcommand{\CVItem}[2]{\textbf{#1} & #2 \\}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\begin{document}

% ===================== Header =====================
{\LARGE \textbf{Mahriar Gharaghani}}\\[-2pt]
{\color{gray}Research-Oriented Curriculum Vitae}\\[4pt]

\begin{tabularx}{\textwidth}{@{}L{3.2cm}Y@{}}
Email & \Link{mailto:mahriargharaghani@gmail.com}{mahriargharaghani@gmail.com} \\
Phone & +98 917 397 8579 \\
Location & Tehran, Iran \\
GitHub & \Link{https://github.com/UDynamic}{github.com/UDynamic} \\
LinkedIn & \Link{https://linkedin.com/mahriar-gharaghani}{linkedin.com/mahriar-gharaghani} \\
Research Areas & Artificial Intelligence, Reinforcement Learning, Decision Intelligence, Operations Research-inspired AI Systems \\
\end{tabularx}

% ===================== Research Profile =====================
\section*{Research Profile}
Research-oriented AI engineer with academic and practical experience at the intersection of
artificial intelligence, sequential decision-making, and project-oriented resource allocation.
Current work focuses on the design of intelligent decision-support systems for project portfolio budgeting
under uncertainty and dynamic cash-flow constraints, combining simulation, optimization, and reinforcement learning.
Prior professional experience in project control and project management has provided the applied context
that motivates this research direction.

% ===================== Research Interests =====================
\section*{Research Interests}
\begin{tabularx}{\textwidth}{@{}L{4.2cm}Y@{}}
Core Interests &
Reinforcement learning, sequential decision-making under uncertainty, optimization-informed AI, simulation-based evaluation, decision-support systems \\
Application Domains &
Project portfolio management, budget allocation, cash-flow constrained planning, industrial and organizational decision systems \\
Related Technical Interests &
Retrieval-augmented generation (RAG), LLM-based workflow systems, ML systems engineering, AI-assisted knowledge tools \\
\end{tabularx}

% ===================== Education =====================
\section*{Education}
\begin{longtable}{@{}L{2.7cm}L{5.7cm}L{2.6cm}Y@{}}
\toprule
\textbf{Degree} & \textbf{Institution} & \textbf{Dates} & \textbf{Details} \\
\midrule
M.Sc. in Engineering Management
& Iran University of Science and Technology (IUST), Tehran, Iran
& 2023--2026
& \textbf{In progress}. Thesis: \textit{Autonomous Budgeting AI Agent}. Research concerns project portfolio budget allocation under uncertainty and dynamic financial constraints using a Python-based deep reinforcement learning framework. The work is evaluated against a perfect-foresight optimization benchmark and has received external support under a contract with \textbf{Tehran Industrial Estates Company}. \\

B.Sc. in Industrial Engineering
& Isfahan University of Technology (IUT), Isfahan, Iran
& 2017--2023
& Completed. Undergraduate training in industrial engineering provided the analytical foundation for later work in planning, decision systems, and quantitative modeling. \\

Ph.D. Entrance Exam (Computer Engineering --- AI \& Robotics)
& National Universities of Iran
& 2026
& Results pending. Preparation process included structured review and implementation work in data structures and algorithms, machine learning, and pattern recognition. Developed the \textbf{RAG4Konkur} study system to support preparation. \\
\bottomrule
\end{longtable}

% ===================== Research Experience =====================
\section*{Research Experience}
\begin{longtable}{@{}L{4.1cm}L{2.4cm}Y@{}}
\toprule
\textbf{Role / Context} & \textbf{Dates} & \textbf{Description} \\
\midrule
M.Sc. Thesis Researcher, IUST
& 2023--2026
& Conducting graduate research on AI-based project portfolio budget allocation under uncertainty and dynamic cash-flow constraints. The research formulates the problem as a sequential decision process and investigates the use of reinforcement learning for adaptive allocation policies. The implementation includes Python-based experimentation, simulation design, and comparison with a perfect-foresight optimization benchmark as an upper bound. \\

Industry-Supported Research Context
& 2023--2026
& Thesis work supported under a contract with \textbf{Tehran Industrial Estates Company}, indicating institutional relevance of the problem setting and its practical value for real-world budgeting and planning environments. \\
\bottomrule
\end{longtable}

% ===================== Research / Technical Projects =====================
\section*{Selected Research and Technical Projects}
\begin{longtable}{@{}L{4.3cm}L{2.1cm}Y@{}}
\toprule
\textbf{Project} & \textbf{Period} & \textbf{Description} \\
\midrule
Autonomous Budgeting AI Agent
& 2023--present
& Developed a research-oriented system for sequential budget allocation in project portfolios subject to uncertainty and changing financial constraints. The project combines domain-informed formulation, simulation-based evaluation, and reinforcement learning. \\

RAG4Konkur
& 2025--2026
& Developed a local retrieval-augmented study assistant for flashcard generation, concept review, and AnkiDroid-ready export. The system was designed to support exam preparation workflows while exploring practical RAG pipeline design and local AI deployment. \\

End-to-End House Price ML Pipeline
& 2024
& Implemented a full machine learning workflow including preprocessing, feature engineering, model development, evaluation, and structured reporting as part of ML systems preparation. \\

PyTorch CIFAR-10 Pipeline
& 2024
& Implemented an image-classification pipeline using PyTorch, including custom data loading, augmentation, checkpointing, and ResNet18 transfer learning. \\

Model Serving with FastAPI and Docker
& 2024
& Designed a deployable inference workflow by exposing a machine learning model through a FastAPI REST interface and containerizing the application using Docker. \\

Robotic Arm Reinforcement Learning Simulation
& 2024
& Explored reinforcement learning in a simulated control setting through a robotic arm task, as part of broader interest in sequential control and decision-making systems. \\

Decision-Support and Visualization Tools
& 2023--present
& Developed several applied prototypes including logistics heatmap tools, live stock visualization systems, spreadsheet-style web utilities, and workflow-oriented AI applications. These projects contributed to practical systems design, interface development, and applied analytical tooling. \\
\bottomrule
\end{longtable}

% ===================== Professional Experience =====================
\section*{Professional Experience}
\begin{longtable}{@{}L{4.3cm}L{2.0cm}Y@{}}
\toprule
\textbf{Position} & \textbf{Dates} & \textbf{Description} \\
\midrule
Project Management Officer, Iran Energy Industries Corporation (IEIC)
& 2023
& Worked in a project-management environment with exposure to organizational planning, reporting, and coordination processes. Served as senior deputy to the Head of Department. This role further strengthened interest in structured decision-making and complex project environments. \\

Project Control Specialist, Jahanpars Group
& 2019--2020
& Contributed to project control activities while still an undergraduate student. This early experience in a large industrial setting, during the COVID-19 period, played an important role in shaping later research interest in planning, uncertainty, and resource allocation. \\

Independent Technical Reorientation
& 2023--present
& Undertook a deliberate transition from management-oriented roles toward technical and research-driven AI systems development. This period included intensive self-directed work in software engineering, machine learning systems, deployment practices, and AI application development. \\
\bottomrule
\end{longtable}

% ===================== Technical Preparation =====================
\section*{Technical Preparation and Independent Study}
\begin{tabularx}{\textwidth}{@{}L{4.2cm}Y@{}}
Software Engineering &
Completed substantial self-directed study in web and software engineering, including responsive web design, JavaScript algorithms and data structures, front-end libraries, data visualization, relational databases, and back-end APIs. \\
ML Systems Preparation &
Worked on model development pipelines, deployment workflows, API serving, containerization, and experiment-tracking concepts relevant to practical ML engineering. \\
AI Application Development &
Explored LangChain-based systems, RAG pipelines, workflow automation, and local AI tool development for domain-specific use cases. \\
\end{tabularx}

% ===================== Skills =====================
\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}L{4cm}Y@{}}
Programming Languages & Python; JavaScript; TypeScript \\
Scientific / Technical Writing & \LaTeX; Markdown \\
Backend and APIs & FastAPI; Django; Express.js \\
Frontend Development & React.js \\
Machine Learning / AI & Machine learning; deep learning workflows; reinforcement learning exposure; prompt engineering; LangChain; retrieval-augmented generation (RAG) \\
Data Work & Exploratory data analysis; preprocessing; feature engineering; data visualization \\
Deployment / Systems & Docker; model serving; deployment concepts; experiment tracking concepts \\
Workflow / Automation & N8N-style automation workflows; AI-assisted process tooling \\
\end{tabularx}

% ===================== Certifications =====================
\section*{Certifications and Structured Training}
\begin{tabularx}{\textwidth}{@{}L{4.2cm}Y@{}}
freeCodeCamp (selected tracks) &
Responsive Web Design; JavaScript Algorithms and Data Structures; Front End Development Libraries; Data Visualization; Relational Database; Back End Development and APIs \\
\end{tabularx}

% ===================== Languages =====================
\section*{Languages}
\begin{tabularx}{\textwidth}{@{}L{3.5cm}Y@{}}
Persian & Native \\
English & Near-native / professional proficiency \\
\end{tabularx}

\end{document}
